Scalable Extreme Deconvolution

### 2019-10-30 ml4ps_paper/paper.tex
Final paper tweaks.

\subsubsection*{Acknowledgments}
We are grateful to David W. Hogg for providing us with the problem and advising us on our experimental setup.
Our experiments made use of AstroPy~\citep{astropy:2013,astropy:2018}, corner.py~\citep{corner}, Numpy~\citep{numpy}, Pandas~\citep{mckinney-proc-scipy-2010}, PyTorch~\citep{paszke2017automatic} and Scikit-learn~\citep{scikit-learn}.
This work was supported in part by the EPSRC Centre for Doctoral Training in Data Science, funded by the UK Engineering and Physical Sciences Research Council (grant EP/L016427/1) and the University of Edinburgh.

@@

Here we provide specific details of our experiments for reproducibility.
Code used to run the experiments will be made available.

>>>>

\subsubsection*{Acknowledgments}
We are grateful to David W. Hogg for providing us with the problem and advising us on the Gaia data.
Our experiments made use of AstroPy~\citep{astropy:2013,astropy:2018}, corner.py~\citep{corner}, Matplotlib~\citep{Hunter:2007}, Numpy~\citep{numpy}, Pandas~\citep{mckinney-proc-scipy-2010}, PyTorch~\citep{paszke2017automatic} and Scikit-learn~\citep{scikit-learn}.
This work was supported in part by the EPSRC Centre for Doctoral Training in Data Science, funded by the UK Engineering and Physical Sciences Research Council (grant EP/L016427/1) and the University of Edinburgh.

@@

Here we provide specific details of our experiments for reproducibility.
Code used to run the experiments is available at \url{https://github.com/bayesiains/scalable_xd}.
